\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-24 lang-design.tex
Save Language Design.
Adding "accessing family components outside that family" into lang-design section Slight change on syntactic translation section.

First and foremost, \textlabel{Req (0)}{langdesign-req0}\textbf{we desire incremental(modular) type checking}. Notice that, the modularity here in Coq is a bit different from other language, because Coq is \textit{interactive} theorem proving so we actually need \textit{statement-wise} incremental type checking, not only for saving the compilation time, but also for the immediate feedback and type-checking for the Coq developer.

@@

This incomplete support can already be helpful for extending functions. Take \cref{fig:plugin-example2} as example, if we want to extend boolean inductive type and its negation, we only need to specify the new constructor for boolean and how negation deal with the new constructor.

>>>>

First and foremost, we don't want to throw away some basic good properties from Coq. \textlabel{Req (0A)}{langdesign-req0}~\textbf{we want to retain the incremental(modular) type checking}. Notice that, the modularity here in Coq is a bit different from other language, because Coq is \textit{interactive} theorem proving so we actually need \textit{statement-wise} incremental type checking, not only for saving the compilation time, but also for the immediate feedback and type-checking for the Coq developer. We don't want our family to ruin this conventional routine of interactive development. \textlabel{Req (0B)}{langdesign-req0b}~\textbf{we also want to keep the computational property of Coq when use family}. Coq, as a constructive logic, has been famous for its ability to do calculations and extract programs. We don't want our Family facility to ruin this: the developers should be able to project field as first-class value just like Coq's Module.

@@

This incomplete support can already be helpful for extending functions. Take \cref{fig:plugin-example2} as example, if we want to extend boolean inductive type and its negation, we only need to specify the new constructor for boolean and how negation deal with the new constructor. This support provides the user a way to waive the necessity for duplicating code -- otherwise the user will need to copy and paste the whole original negation definition and add a new pattern matching cases.
